---
title: "Summary Statistics"
author: "Joy Lin"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())

# Required libraries
library(dplyr)
library(readstata13)
```

### Christmas campaign data
```{r}
county_data_X = readxl::read_excel("../Data/randomized_sample_christmas.xlsx")
county_data_X= distinct(county_data_X[,c("fips","high_county")])
colnames(county_data_X) = c("user_loc","high_county_X")
```

### Thanksgiving campaign data
```{r}
county_data_T1 = readxl::read_excel("../Data/randomized_sample_thanksgiving.xlsx")
county_data_T1 = county_data_T1 %>% group_by(county) %>% mutate(share_urban = mean(urban))
county_data_T1 = distinct(county_data_T1[,c("county","high_county","share_urban")])
colnames(county_data_T1) = c("user_loc","high_county_T1","share_urban") 
```

### Merging Christmas and Thanksgiving data
```{r}
county_data = merge(county_data_X,county_data_T1,by="user_loc",all=TRUE)
```

### Data containing the movement variables
```{r}
facebook_data = read.dta13("../Data/fb_movement_data.dta")
colnames(facebook_data)=c("user_loc","county", "movement_ch", "stay_home", "date") 
facebook_data$user_loc=as.numeric(facebook_data$user_loc)
```

### Population in each county in 2019
```{r}
county_pop2019 = read.dta13("../Data/county_pop2019.dta")
colnames(county_pop2019) = c("popestimate2019", "user_loc")  
county_pop2019$user_loc=as.numeric(county_pop2019$user_loc)
```

### Covid data at county level
```{r}
covid_counties = read.csv("../Data/us-counties.csv")
colnames(covid_counties) = c("date", "county", "state", "user_loc", "cases",  "deaths")
covid_counties$user_loc = as.numeric(covid_counties$user_loc)
```

### Covariates
```{r}
county_covariates = read.dta13("../Data/county_covariates.dta")
names(county_covariates)[names(county_covariates) == 'fips'] = 'user_loc'

# Proportions for covariates
for (var in c("white","asian","islander","raceother","pop18_24","p18_24nohs",
              "p18_24hs","p18_24somecoll","p18_24bacc","g25","nohsg25","nodegreeg25","hsg25",
              "somecollg25","assocg25","baccg25","graduatedegreeg25","g65","hsg65",
              "baccorhigherg65", "povmale","povfemale","povwhite","povindig","povasian", 
              "povislander","povraceother","povsomecollege","povbaccorhigher","utotal")){
  county_covariates[[paste0("prop",var)]]=county_covariates[[var]]/county_covariates$population
}

covariates = colnames(county_covariates)[grepl("prop", colnames(county_covariates), fixed=TRUE)]
```

### Election data
```{r}
Election_data = read.dta13("../Data/Election2020.dta")

Election_data=Election_data[,c("fips2","per_gop","per_dem")]
colnames(Election_data)=c("user_loc","per_gop","per_dem")
```

### Merge data
```{r}
# Merging county population
data = merge(county_data,county_pop2019,by = "user_loc")
# Merging covid cases by counties
data = merge(data,covid_counties,by = "user_loc",all.x=TRUE)
data$date = as.Date(data$date, origin = "1960-01-01") 
# Merging facebook data
data = merge(data,facebook_data,by=c("user_loc","date"),all=TRUE)
# Merging covariates
data = merge(data, county_covariates, by = "user_loc",all.x=TRUE)
# Merging election data
data = merge(data,Election_data,by="user_loc",all.x=TRUE)
```

### Keeping recent data (Past 10/1/2020)
```{r}
data = data %>% filter(date >= "2020-10-01") 
```

### Baseline variable
```{r}
data$leave_home = 1 - data$stay_home

data$leave_home = 100*data$leave_home
data$movement_ch = 100*data$movement_ch

data = data %>%
  group_by(user_loc) %>% 
  mutate(
    baseline_th_leave_home=ifelse(as.numeric(as.Date("2020/11/13")) %in% as.numeric(date),leave_home[as.numeric(date)==as.numeric(as.Date("2020/11/13"))],NA),
    baseline_th_movement_ch=ifelse(as.numeric(as.Date("2020/11/13")) %in% as.numeric(date),movement_ch[as.numeric(date)==as.numeric(as.Date("2020/11/13"))],NA),

    baseline_th_cases = ifelse(as.numeric(as.Date("2020/11/13")) %in% as.numeric(date),cases[as.numeric(date)==as.numeric(as.Date("2020/11/13"))],NA),
    baseline_th_deaths = ifelse(as.numeric(as.Date("2020/11/13")) %in% as.numeric(date),deaths[as.numeric(date)==as.numeric(as.Date("2020/11/13"))],NA),
    
    pre_baseline_th_cases= ifelse(as.numeric(as.Date("2020/10/31")) %in% as.numeric(date),cases[as.numeric(date)==as.numeric(as.Date("2020/10/31"))],NA),
    pre_baseline_th_deaths= ifelse(as.numeric(as.Date("2020/10/31")) %in% as.numeric(date),deaths[as.numeric(date)==as.numeric(as.Date("2020/10/31"))],NA),
  )


data$missing_baseline_leave_home = is.na(data$baseline_th_leave_home)
data$missing_baseline_movement = is.na(data$baseline_th_movement_ch)

data$bl_fortnightly_cases = data$baseline_th_cases-data$pre_baseline_th_cases
data$bl_fortnightly_deaths = data$baseline_th_deaths-data$pre_baseline_th_deaths


variables_for_table =  c("popestimate2019",     
                         "baseline_th_movement_ch",
                         "baseline_th_leave_home" ,  
                         "bl_fortnightly_cases",
                         "bl_fortnightly_deaths",
                         "missing_baseline_movement",
                         "share_urban",
                         "per_dem",
                         "per_gop")


labels = c("Population in 2019",
           "Baseline Movement Metric",
           "Baseline Leave Home",
           "Baseline Fortnightly Cases",
           "Baseline Fortnightly Deaths",
           "Missing Baseline Facebook outcomes",
           "Share Urban",
           "Share Democrats",
           "Share Republicans")
```

## Thanksgiving sample
```{r}
data_table = data %>% filter(!is.na(high_county_T1))
data_table = data_table[,c("user_loc","high_county_T1",variables_for_table)]
data_table =  distinct(data_table)

panels = list(data_table,data_table[data_table$high_county_T1==1,],data_table[data_table$high_county_T1==0,])
```

### Generation of Thanksgiving summary table
```{r}
# list of the means
mean_lines = c()
i=1
for (panel in panels){
  # counting the number of observations
  mean_lines = c(mean_lines,nrow(panel))
  for (var in variables_for_table){
  # for continuous variable, computing mean
      mean_lines = c(mean_lines,paste0(format(round(mean(panel[[var]],na.rm=TRUE), digits=2), nsmall = 2)))
  }
  i=i+1
}

# list of the standard deviations
sd_lines = c()
j = 1
for (panel in panels){
  # counting the number of observations
  sd_lines = c(sd_lines,nrow(panel))
  for (var in variables_for_table){
  # for continuous variable, computing sd
      sd_lines = c(sd_lines,paste0(format(round(sd(panel[[var]],na.rm=TRUE), digits=2), nsmall = 2)))
  }
  i=i+1
}

# creating data frame
table1 = data.frame(mean_lines[1:10], sd_lines[1:10], 
                    mean_lines[11:20], sd_lines[11:20],
                    mean_lines[21:30], sd_lines[21:30],
                    row.names = c("Number of observations", labels))

# changing column names
colnames(table1) = c("Mean of Thanksgiving Sample", "Standard Deviation of Thanksgiving Sample",
                     "Mean of High-intensity counties", "Standard Deviation of High-intensity counties", 
                     "Mean of Low-intensity counties", "Standard Deviation of Low-intensity counties")

# Removing number of observations and making it separate from table
nb_sample = table1$`Mean of Thanksgiving Sample`[1]
nb_high = table1$`Mean of High-intensity counties`[1]
nb_low = table1$`Mean of Low-intensity counties`[1]
print(paste0("The number of observations in the Thanksgiving sample is ", nb_sample))
print(paste0("The number of observations in the Thanksgiving high-intensity counties sample is ", nb_high))
print(paste0("The number of observations in the Thanksgiving low-intensity counties sample is ", nb_low))

table1 = table1[-1,]

table1
View(table1)
```

## Christmas sample
```{r}
data_table = data %>% filter(!is.na(high_county_X)) 
data_table = data_table[,c("user_loc","high_county_X",variables_for_table)]
data_table =  distinct(data_table)

panels = list(data_table,data_table[data_table$high_county_X==1,],data_table[data_table$high_county_X==0,])
```

### Generation of Christmas summary table
```{r}
# list of the means
mean_lines = c()
i=1
for (panel in panels){
  # counting the number of observations
  mean_lines = c(mean_lines,nrow(panel))
  for (var in variables_for_table){
  # for continuous variable, computing mean
      mean_lines = c(mean_lines,paste0(format(round(mean(panel[[var]],na.rm=TRUE), digits=2), nsmall = 2)))
  }
  i=i+1
}

# list of the standard deviations
sd_lines = c()
j = 1
for (panel in panels){
  # counting the number of observations
  sd_lines = c(sd_lines,nrow(panel))
  for (var in variables_for_table){
  # for continuous variable, computing sd
      sd_lines = c(sd_lines,paste0(format(round(sd(panel[[var]],na.rm=TRUE), digits=2), nsmall = 2)))
  }
  i=i+1
}

# creating data frame
table2 = data.frame(mean_lines[1:10], sd_lines[1:10], 
                    mean_lines[11:20], sd_lines[11:20],
                    mean_lines[21:30], sd_lines[21:30],
                    row.names = c("Number of observations", labels))

# changing column names
colnames(table2) = c("Mean of Christmas Sample", "Standard Deviation of Christmas Sample",
                     "Mean of High-intensity counties", "Standard Deviation of High-intensity counties", 
                     "Mean of Low-intensity counties", "Standard Deviation of Low-intensity counties")

# Removing number of observations and making it separate from table
nb_sample = table2$`Mean of Christmas Sample`[1]
nb_high = table2$`Mean of High-intensity counties`[1]
nb_low = table2$`Mean of Low-intensity counties`[1]
print(paste0("The number of observations in the Christmas sample is ", nb_sample))
print(paste0("The number of observations in the Christmas high-intensity counties sample is ", nb_high))
print(paste0("The number of observations in the Christmas low-intensity counties sample is ", nb_low))

table2 = table2[-1,]

table2
View(table2)
```
